### 2017-12-19 Paper/DGSM_PCE_MD_paper.tex
moved cover to a separate file

\begin{center}
\textsc{
Efficient derivative-based global sensitivity approach to 
surrogate modeling with application to molecular dynamics
}

\bigskip

\bigskip

Manav Vohra, Alen Alexanderian, Sankaran Mahadevan

\end{center}

\vspace{10cm}

\begin{tabular}{ll}
Corresponding Author:  & TBA \\
                       & Vanderbilt University \\ 
                       & Nashville, TN\\ 
                       & Phone: \\ 
                       & Email: 
\end{tabular}

\bigskip

Submitted to: \emph{Journal of Computational Physics}

\clearpage

>>>>

\input{cover}

### 2017-12-19 Paper/cover.tex
moved cover to a separate file

%-------------------COVER-------------------------------------------
\begin{center}
\begin{Large}
{\bf Bayesian Guided Optimal Experimental Design for Reactive Multilayers}\\
\end{Large}

\bigskip
%\bigskip

Manav Vohra,$^1$ Xun Huan,$^2$ Omar M. Knio$^{1,3}$ \\

\bigskip
\bigskip

\normalsize
$^1$Department of Mechanical Engineering and Materials Science\\
Duke University\\
Durham, NC 27708\\

@@

$^2$Department of Aeronautics and Astronautics\\
Massachusetts Institute of Technology\\
Cambridge, MA 02139\\

@@

$^3$Computer, Electrical and Mathematical Sciences and Engineering Division \\
King Abdullah University of Science and Technology \\
Thuwal 23955-6900, Kingdom of Saudi Arabia\\

@@

\vspace{6cm}

\begin{tabbing}
Corresponding Author: \hspace{5mm} \= Omar M. Knio\\
       \>  Department of Mechanical Engineering and Materials Science\\
       \>  Duke University\\
       \>  144 Hudson Hall, Box 90300 \\
       \>  Durham, NC 27708 \\
       \> \\
Phone: \> (919) 660-5344 \\
Fax:   \> (919) 660-8963 \\
Email: \>  omar.knio@duke.edu   \\
\\
Submitted to: \> \textit{Journal} \\
\> December 2015\\

\end{tabbing}
\clearpage

>>>>

\begin{center}
\textsc{
Derivative-based global sensitivity approach to 
efficient surrogate modeling with application to molecular dynamics
}

@@

@@

Manav Vohra, Alen Alexanderian, Sankaran Mahadevan

@@

\vspace{10cm}

\begin{tabular}{ll}
Corresponding Author:  & TBA \\
                       & Vanderbilt University \\ 
                       & Nashville, TN\\ 
                       & Phone: \\ 
                       & Email: 
\end{tabular}

Submitted to: \emph{Journal of Computational Physics}

\clearpage
